Testing atlantisom: generate survey sampled length comps

### 2019-05-14 StdSurvLengthCompTest.Rmd
add census-sample lf comparison

```{r allspplengthsamp}

@@

Comparison plots for other species:

```{r moreplots, echo=TRUE, eval=FALSE}

ss_length_censussurvsamp <- length_censussurvsamp$natlength %>%
  filter(species == "Herring")

@@

# add sample, this is census, probably want it first?
lfplot <- ggplot(ss_length_censussurvsamp, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte()

@@

>>>>

```{r allspplengthsamp, eval=FALSE}

@@

Comparison plots for other species. Blue bars are the census length sample and red outlines are the survey sample (standardized for comparison; census total n lengths is 1e+8 while sample total n lengths is 1000):

```{r moreplots, echo=TRUE}

# select a species
ss_length_censussurvsamp <- length_censussurvsamp$natlength %>%
  filter(species == "Herring")

@@

# make proportion at length to plot together
lf_census_tot <- aggregate(ss_length_censussurvsamp$atoutput,list(ss_length_censussurvsamp$time),sum )
names(lf_census_tot) <- c("time","totlen")

lf_census_prop <- merge(ss_length_censussurvsamp, lf_census_tot)

lf_samp_tot <- aggregate(ss_length_stdsurv$atoutput,list(ss_length_stdsurv$time),sum )
names(lf_samp_tot) <- c("time","totsamp")

lf_samp_prop <- merge(ss_length_stdsurv, lf_samp_tot)

# add sample, this is census, probably want it first?
lfplot <- ggplot(mapping=aes(x=upper.bins)) +
  geom_bar(data=lf_census_prop, aes(weight = atoutput/totlen), fill="blue") +
  geom_bar(data=lf_samp_prop, aes(weight = atoutput/totsamp), colour="red") +
  theme_tufte()

@@

Here as with [cohort sampling](https://sgaichas.github.io/poseidon-dev/StdSurvLengthAgeCompTest.html), the impact of survey selectivity is much larger than sampling error with effN of 1000. We could try effN that is lower, but 1000 lengths may be reasonable from a survey. A `sample_lengths` function could add further measuremet error on top of this, if desired (though measurement error at the 1 cm level may be negligible).
